intro

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/TheoreticalBackground.Rmd
placeholder for figures
moved figure to end of document

```{r ResponsePatterns, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Exemplary visualization of two response patterns. In the top half, the person has a clear preference for one of the three strategies. In the lower half, they have no clear preference and therefore show an inconsistent response pattern. This pattern can be represented by our paradigm."}
include_graphics(here("06_Paper", "ER-ED", "figures", "Paradigm_Scheme_T2.png" ))
```

>>>>

[INSERT FIGURE 1 HERE]
